\thesistitle

### 2019-05-03 sattose/paper.tex
Wrote some stuff
Something about type 4 clones

A higher type of clone means that it's harder to detect. It also makes the clone harder to refactor, as more transformations would be required. Higher clone types also become more disputable whether they actually indicate a harmful antipattern (as not every clone is harmful \cite{jarzabek2010clones, kapser2008cloning}). Type 1 clones are most often, if not always with the right thresholds, harmful. Type 2 and type 3 clones are more disputable whether they are harmful and whether they can be merged in a way that improves the design of the code. In this chapter, we will redefine type 2 and type 3 clones to increase the chance that we can merge the clone while improving the design. Type-4 clones are, because of the serious challenges involved in their detection and refactoring, out of the scope for this study.

>>>>

A higher type of clone means that it's harder to detect. It also makes the clone harder to refactor, as more transformations would be required. Higher clone types also become more disputable whether they actually indicate a harmful antipattern (as not every clone is harmful \cite{jarzabek2010clones, kapser2008cloning}). Type 1 clones are most often, if not always with the right thresholds, harmful. Type 2 and type 3 clones are more disputable whether they are harmful and whether they can be merged in a way that improves the design of the code. In this chapter, we will propose solution for shortcomings in type 1, type 2 and type 3 clones to increase the chance that we can merge the clone while improving the design. Type-4 clones are, because of the serious challenges involved in their detection and refactoring, out of the scope for this study.

### 2019-05-03 sections/background.tex
Something about type 4 clones

Relating this to the clone class example of \ref{fig:cloneclass}, the complete class would be flagged as a type 2 clone. This is displayed in figure \ref{fig:type2cloneclass}. Considering such clones displays the opportunity to refactor the class as a whole.

@@

For this thesis we have chosen not to consider type 4 clones for refactoring, because they are both hard to detect and hard to refactor (how to choose the best alternative for a certain computation could be a thesis in itself).

>>>>

\subsection{Type 2 clones}
Relating this to the clone class example of \ref{fig:cloneclass}, the complete class would be flagged as a type 2 clone. This is displayed in figure \ref{fig:type2cloneclass}. Considering such clones displays the opportunity to refactor the class as a whole.

@@

\subsection{Type 4 clones}
For this thesis we have chosen not to consider type 4 clones for refactoring, because they are both hard to detect and hard to refactor (how to choose the best alternative for a certain computation could be a thesis in itself). A study by Kodhai et al \cite{kodhai2013method} looks into the distribution of the different types of clones in several open source systems (see table 6 of his study). It becomes apparent that type 4 clones exist way less in source code than all of the other types of clones. For instance, for the J2sdk-swing system he finds  8115 type 1 clones, 8205 type 2 clones, 11209 type 3 clones and only 30 type 4 clones. Because of that, we can conclude that type 4 clones are relatively less relevant to study.

### 2019-05-03 sections/research.tex
:full_moon_with_face:
Something about type 4 clones

\chapter{Clone Detection}
As duplication in source code is a serious problem in many software systems, there are a lot of researches that look into code clones. Many tools have been proposed to detect various types of code clones. Two surveys of modern clone detection tools \cite{sheneamer2016survey, svajlenko2014evaluating} together show an overview of the most-popular clone detection tools up until 2016. To be able to refactor detected clones, it is useful to have the ability to rewrite the AST. We considered a set of clone detection tools for their ability to support the refactoring process automatically. None of the tools we consider seemed completely fit for this purpose, so we decided to implement our own clone detection tool: CloneRefactor\footnote{CloneRefactor (WIP) is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}.

\chapter{Redefining type 1, 2 and type 3 clones}
In a 2007 survey by Roy et al \cite{roy2007survey} he defined four types of clones:

\textbf{Type 1:} Identical code fragments except for variations in whitespace (may be also variations in layout) and comments.\\
\textbf{Type 2:} Structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments.\\
\textbf{Type 3:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout, and comments.\\
\textbf{Type 4:} Two or more code fragments that perform the same computation but implemented through different syntactic variants.

A higher type of clone means that it's harder to detect. It also makes the clone harder to refactor, as more transformations would be required. Higher clone types also become more disputable whether they actually indicate a harmful antipattern (as not every clone is harmful \cite{jarzabek2010clones, kapser2008cloning}). Type 1 clones are most often, if not always with the right thresholds, harmful. Type 2 and type 3 clones are more disputable whether they are harmful and whether they can be merged in a way that improves the design of the code. In this chapter, we will redefine type 2 and type 3 clones to increase the chance that we can merge the clone while improving the design. Type-4 clones are, because of the serious challenges involved in their detection and refactoring, out of the scope for this study.

\section{Type 1 clones}
Type 1 clones are identical clone fragments except for variations in whitespace and comments. However, when two clone fragments are textually identical, does not yet indicate that they are actually identical. Even when textually equal, method calls can refer to different methods, type declarations can refer to different types and even variables can be of a different type. This could invalidate a refactoring opportunity for such a code fragment. Because of that, we recommend redefining type-1 clones for refactoring. We propose to:
\begin{itemize}
  \item \textbf{Compare the equality of the fully qualified method signature for method references.} This way we can validate whether two method references, like method calls, are actually equal. In the method signature, not only the fully qualified identifier of the method should be considered, but also of the type of all its arguments. This way we can be sure that two potentially cloned method references do not point to overloaded variants (in a case that the data type of arguments is overloaded).
  \item \textbf{Compare the equality of the fully qualified identifier for type references.} This way we can be sure that two referenced types are actually equal, and that they are not just two types with the same name.
  \item \textbf{Compare the equality the fully qualified identifier for variable usages.} Two cloned lines might use a variable with the same name, but different types. This might pose serious challenges on refactoring, as the variables might not concern the same object or primitive. To check this, we need to track the declaration of variables and from this infer the fully qualified identifier of its type.
\end{itemize}

@@

>>>>

\chapter{Redefining type 1, 2 and type 3 clones}
In the background section we discussed the different types of clones, as defined by Roy et al \cite{roy2007survey}. However, when detecting clones by these definitions, we will detect many clones that are not immediately useful for refactoring. In this chapter, we will discuss the shortcoming of each of the clone types, and propose solutions for them.

\section{Type 1 clones}
Type 1 clones are identical clone fragments except for variations in whitespace and comments. However, when two clone fragments are textually identical, does not yet indicate that they are actually identical. Even when textually equal, method calls can refer to different methods, type declarations can refer to different types and even variables can be of a different type.

This could invalidate a refactoring opportunity for such a code fragment. Because of that, we recommend redefining type-1 clones for refactoring. We propose to:
\begin{itemize}
  \item \textbf{Compare the equality of the fully qualified method signature for method references.} This way we can validate whether two method references, like method calls, are actually equal. In the method signature, not only the fully qualified identifier of the method should be considered, but also of the type of all its arguments. This way we can be sure that two potentially cloned method references do not point to overloaded variants (in a case that the data type of arguments is overloaded).
  \item \textbf{Compare the equality of the fully qualified identifier for type references.} This way we can be sure that two referenced types are actually equal, and that they are not just two types with the same name.
  \item \textbf{Compare the equality the fully qualified identifier for variable usages.} Two cloned lines might use a variable with the same name, but different types. This might pose serious challenges on refactoring, as the variables might not concern the same object or primitive. To check this, we need to track the declaration of variables and from this infer the fully qualified identifier of its type.
\end{itemize}

@@

\chapter{Clone Detection}
As duplication in source code is a serious problem in many software systems, there are a lot of researches that look into code clones. Many tools have been proposed to detect various types of code clones. Two surveys of modern clone detection tools \cite{sheneamer2016survey, svajlenko2014evaluating} together show an overview of the most-popular clone detection tools up until 2016. We have considered a set of these tools. However, most of these tools have a vastly different purpose than this thesis. Most of the tools are focussed on efficiency and detecting all of the types of clones. Efficiency is lesser of a concern to us, correctness is the most important aspect.

To be able to refactor detected clones, it is useful to have the ability to rewrite the AST. We considered a set of clone detection tools for their ability to support the refactoring process automatically. None of the tools we consider seemed completely fit for this purpose, so we decided to implement our own clone detection tool: CloneRefactor\footnote{CloneRefactor (WIP) is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}.
